\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2013-09-04 paper.tex
Fix path for figures
Required for Elsevier submission
Removed Aurelie and Mathieu from authors

\author{Rachid Alami, Séverin Lemaignan, Aurélie Clodic, Mathieu Warnier}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\columnwidth]{figs/grounding_robot.pdf}
\caption{Robot reasoning about HRI and anticipation of human activities:
  sources of information are multi-modal dialogue, and observation of
  environment and human activity}
\label{fig:hri-dec}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
    \subfigure[] { \includegraphics[width=0.2\textwidth]{figs/reachex-1.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{figs/reachex-2.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{figs/reachex-3.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{figs/reachex-4.jpg} }
	\caption{An example illustrating the \textit{reachable} relation. The relation is computed from the perspectives of both the robot and the human. The computed posture at each step is illustrated with a global view of the scene (top), and from a closest view (bottom).}
\label{fig::reach-ex}
\end{figure*}

\begin{figure*}[ht!]
   \begin{center}
%
       \subfigure[Initial state]{%
%           \label{fig:wuweiPhoto}
           \includegraphics[width=0.5\textwidth]{./figs/etat2-P1010769_brightened-v2.jpg}
       }%
       \subfigure[3d model view of initial state]{%
%          \label{fig:sparkScreenshot}
          \includegraphics[width=0.43\textwidth]{./figs/etat2_photo.png}
       }\\ %  ------- End of the first row ----------------------%
%
   \end{center}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\columnwidth]{./figs/first_plan.pdf}
  \caption{A plan produced by HATP with 2 streams}
  \label{plan_hatp1}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\columnwidth]{./figs/second_plan.pdf}
  \caption{A plan with the wasted time social rule}
  \label{plan_hatp2}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.9\linewidth]{./figs/pt.jpg}
\caption{Asking the robot to hand over a tape on the table.}
  \label{fig|vpt}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.9\linewidth]{./figs/inTheBox2.jpg}
\caption{Jerry asks Jido for the content of the box by pointing at it.}
  \label{fig|pointing}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{./figs/cleantable.jpg}

@@

\begin{figure*}[thpb]
  \centering
  \includegraphics[width=1.0\textwidth]{./figs/plan3.pdf} \\
  \caption {A plan produced by HATP to execute the high-level order ``clean the table''. Two streams of actions are generated: for the human (top) and for the robot(bottom). Synchronization points ensure the coordination.}
  \label{plan-etat2}
\end{figure*}

@@

\begin{figure*}[thpb]
  \centering
    \includegraphics[width=1.0\textwidth]{./figs/manip_run.pdf} \\
    \begin{center}
        \caption {Sequence of events of a simplified version of the \emph{Cleaning the table} scenario.}
    \end{center}
  \label{fig|cleantable-timeline}
\end{figure*}

>>>>

\author{Séverin Lemaignan, Rachid Alami}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.9\columnwidth]{grounding_robot.pdf}
\caption{Robot reasoning about HRI and anticipation of human activities:
  sources of information are multi-modal dialogue, and observation of
  environment and human activity}
\label{fig:hri-dec}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
    \subfigure[] { \includegraphics[width=0.2\textwidth]{reachex-1.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-2.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-3.jpg} }
    \subfigure[] {\includegraphics[width=0.2\textwidth]{reachex-4.jpg} }
	\caption{An example illustrating the \textit{reachable} relation. The relation is computed from the perspectives of both the robot and the human. The computed posture at each step is illustrated with a global view of the scene (top), and from a closest view (bottom).}
\label{fig::reach-ex}
\end{figure*}

\begin{figure*}[ht!]
   \begin{center}
%
       \subfigure[Initial state]{%
%           \label{fig:wuweiPhoto}
           \includegraphics[width=0.5\textwidth]{etat2-P1010769_brightened-v2.jpg}
       }%
       \subfigure[3d model view of initial state]{%
%          \label{fig:sparkScreenshot}
          \includegraphics[width=0.43\textwidth]{etat2_photo.png}
       }\\ %  ------- End of the first row ----------------------%
%
   \end{center}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\columnwidth]{first_plan.pdf}
  \caption{A plan produced by HATP with 2 streams}
  \label{plan_hatp1}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\columnwidth]{second_plan.pdf}
  \caption{A plan with the wasted time social rule}
  \label{plan_hatp2}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.9\linewidth]{pt.jpg}
\caption{Asking the robot to hand over a tape on the table.}
  \label{fig|vpt}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=0.9\linewidth]{inTheBox2.jpg}
\caption{Jerry asks Jido for the content of the box by pointing at it.}
  \label{fig|pointing}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{cleantable.jpg}

@@

\begin{figure*}[thpb]
  \centering
  \includegraphics[width=1.0\textwidth]{plan3.pdf} \\
  \caption {A plan produced by HATP to execute the high-level order ``clean the table''. Two streams of actions are generated: for the human (top) and for the robot(bottom). Synchronization points ensure the coordination.}
  \label{plan-etat2}
\end{figure*}

@@

\begin{figure*}[thpb]
  \centering
    \includegraphics[width=1.0\textwidth]{manip_run.pdf} \\
    \begin{center}
        \caption {Sequence of events of a simplified version of the \emph{Cleaning the table} scenario.}
    \end{center}
  \label{fig|cleantable-timeline}
\end{figure*}
